Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-08-31 documentation/paper.tex
Explained accuracy based on hyperparameters

@@

The following table represents the performance of a variety of iterative cluster nucleation configurations tested during the grid search. As with gravitational differentiation, the accuracy statistic is the mean over three tests of the same configuration.

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Summary of semi-supervised learning systems.}
        \begin{tabular}{|l|l|l|l|l|l|}
            \hline
            Initial $\varsigma$ Size & Technique & Mean AP Accuracy & Mean Precision & Mean Recall & Mean CWSD \\
            \hline
            32 & ICN & 95\% & 94\% & 99\% & 0.38 \\
            \hline
            64 & ICN & 97\% & 96\% & 99\% & 0.28 \\
            \hline
            128 & ICN & 98\% & 98\% & 100\% & 0.21 \\
            \hline
            256 & ICN & 99\% & 99\% & 100\% & 0.15 \\
            \hline
            $\infty$ & AP & 100\% & 100\% & 100\% & TODO \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

>>>>

Interestingly, the four hyperparameters optimized during the grid search were observed to have a weak polynomial correlation with the network's accuracy. This makes the mean accuracy over all configurations a meaningful statistic, since the accuracy for an individual configuration is difficult to confidently predict.

With 32 and 64 examples it was only 75\% and 84\%, respectively, implying that the high maximum accuracy statistics were subject to a high degree of randomness. However, for 128 and 256 initial examples, the mean accuracy statistics over all configurations were 95\% and 97\%, respectively, indicating that the training is much more reliable with a larger initial set.

Note that there are several hyperparameters not specifically optimized in the context of iterative cluster nucleation, including the number of layers and numbers of neurons within those layers. The correlation between those hyperparameters and accuracy is subject to future research.

@@

The following table represents the performance of a variety of high-accuracy iterative cluster nucleation configurations tested during the grid search. As with gravitational differentiation, the accuracy statistic is the mean over three tests of the same configuration.

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Summary of semi-supervised learning systems.}
        \begin{tabular}{|l|l|l|l|l|l|}
            \hline
            Initial $\varsigma$ Size & Technique & Mean AP Accuracy & Mean Precision & Mean Recall & Mean CWSD \\
            \hline
            32 & ICN & 95\% & 94\% & 99\% & 0.38 \\
            \hline
            64 & ICN & 97\% & 96\% & 99\% & 0.28 \\
            \hline
            128 & ICN & 98\% & 98\% & 100\% & 0.21 \\
            \hline
            256 & ICN & 99\% & 99\% & 100\% & 0.15 \\
            \hline
            $\infty$ & AP & 100\% & 100\% & 100\% & 0.41 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}
